\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-11 Papers/ViscousInstabilities/article_figure1.tex
updates

%%%%
%%%%  FIGURE 
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{-0.3cm}
\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{3.5cm} (a) map of permeabilities ($\mathbf{K}$)
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.5cm} (b) flow at t=250 
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (c) flow at t=3000   
}}     
\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$s and t=$300$ sec. The domain is discretised with $5960$ \PN[1]{2} elements. }
\label{fem_cv_represent_a}
\end{figure}
\clearpage

@@

>>>>

%%%%
%%%%  FIGURE 
%%%%
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{-0.3cm}
\includegraphics[width=.8\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_perm_1.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{3.5cm} (a) map of permeabilities ($\mathbf{K}$)
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.85\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_250_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.5cm} (b) flow at t=250 
}
\vspace{0.25cm}
\hbox{\hspace{1.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/2b2_wi_fine/2b2_whole_in_fine_3000_2.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{4.0cm} (c) flow at t=3000   
}}     
\caption{Model validation of fluid displacement in heterogeneous porous media ({\it VR}=1): (a) the domain is divided into four subdomains with prescribed synthetic permeability, $\mathbf{K}_{1}=1$ and $\mathbf{K}_{2}=2.5$; (b-c) snapshots of saturation (displacing fluid) field at t=$25$s and t=$300$ sec. The domain is discretised with $5960$ \PN[1]{2} elements. \red{(ARE YOU SURE TIME IS CORRECT ??)} }
\label{fem_cv_represent_a}
\end{figure}
\clearpage

@@

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-.5cm}
      \hbox{\includegraphics[width=.55\textwidth, height=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D30c} 
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D60c}
            \includegraphics[width=.5\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D90c} }
      \hbox{\hspace{2.0cm} (a) t=XXXs \hspace{6.cm} (b) t=XXXs \hspace{4.cm} (c) t=XXXs}
      \vspace{0.5cm}
      \hbox{\hspace{.5cm} \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D110c}
            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D150c}
            \includegraphics[width=.45\textwidth]{./Pics1/3D_Channel/3D_Channel_Saturation1Isosurface_D300c} }
      \hbox{\hspace{3.cm} (d) t=XXXs \hspace{3.cm} (e) t= XXXs\hspace{4.cm} (f) t=XXXs }}
\caption{XXX.}
\label{fig:3DChannel_Isosurf}
\end{figure}
\end{landscape}
\clearpage
